The \project{UNRAVE} catalog

### 2016-08-12 article/unrave.tex
some shit

\begin{abstract}
On 14 September 2016 the \project{Gaia} mission will release positions, proper motions, and parallaxes for about two million stars.  Most studies intending to make use of those data would benefit enormously from stellar chemical abundances.  The RAdial Velocity Experiment (\project{RAVE}) survey has acquired spectra for approximately 280,000 stars in common with the first \project{Gaia} data release, constituting the largest overlap of any stellar spectroscopic sample.  Here we perform an independent analysis of the \project{RAVE} spectra using a new non-parametric implementation of \thecannon\ that employs prior probabilities on atomic line formation and stellar astrophysical parameters.  We deliver effective temperature $\teff$, surface gravity $\logg$, and chemical abundances of up to 8 elements (Fe, Na, Mg, Al, C, N, Ti, Ca) for \Nstars\ stars.  We validate our results internally from repeat visits, and externally against existing high-resolution spectroscopic surveys.  The typical precision in chemical abundances is $X.XX$~dex.  
\end{abstract}

@@

@@

>>>>

\begin{abstract}
On 14 September 2016 the \project{Gaia} mission will release positions, proper motions, and parallaxes for about two million stars.  Most studies intending to make use of those data would benefit enormously from stellar chemical abundances.  The RAdial Velocity Experiment (\project{RAVE}) survey has acquired spectra for approximately 290,000 stars in common with the first \project{Gaia} data release, constituting the largest overlap of any stellar spectroscopic sample.  Here we perform an independent analysis of the \project{RAVE} spectra using a new non-parametric implementation of \thecannon\ that employs prior probabilities on atomic line formation and stellar astrophysical parameters.  We deliver effective temperature $\teff$, surface gravity $\logg$, and chemical abundances of up to seven elements (Mg, Al, Si, Ca, Ti, Fe, Ni) for \Nstars\ stars.  We validate our results internally from repeat visits, and externally against existing high-resolution spectroscopic surveys.  The typical precision in chemical abundances is $X.XX$~dex.  
\end{abstract}

@@

The first \project{Gaia} data release includes positions, proper motions, and parallaxes for approximately two million stars in the Tycho-2 catalog \citep{tycho2}.  After cross-matching all major stellar spectroscopic surveys\footnote{Specifically we cross-matched the Tycho-2 catalog against {APOGEE} \citep{apogee}, \project{GALAH} \citep{galah}, \project{Gaia-ESO} \citep{ges}, \project{LAMOST} \citep{lamost}, and \project{RAVE} \citep{rave}}, we found the \project{RAVE} survey to have the largest overlap with the first \project{Gaia} data release: 292,036 stars.  We then used the \project{Gaia} universe model to estimate the precision in parallax and proper motions available in \project{Gaia} DR1 for every star in these cross-matches.  Comparing the expected precision to what is currently available, we further found that the \project{RAVE} survey would benefit most from \project{Gaia} DR1.  The distances of 63\% of the \project{RAVE}--\project{Gaia} DR1 overlap sample (182,862 stars) are expected to improve with the first \project{Gaia} data release, and 47\% are likely to have better proper motions (137,211 stars).

This motivated us to examine what chemical abundance information is currently available for \project{RAVE}, and to evaluate whether we could contribute additional abundances.

@@

% Include velocities at test time?
% Train on fibre number? Fit for spectral resolution at test time?
